Coasting on Duality: What We Get When We Do Two-Mode CA

### 2024-03-31 ncsu-presentation.qmd
Updated presentation

## CA Reveals Dual Communities
![](Plots/ca-sim-slide.png)
::: {.notes}

To fix the intuition, the top-left panel (a) of the figure shows a heatmap representation of the group-size weighted similarity matrix $S_p$ (for people); the top-right panel (b) shows the same plot for the activity-weighted similarity matrix $S_g$ (for groups). In both figures, darker squares indicate more similar node pairs, and closer to white indicate less similarity. Moreover, the rows of each matrix are sorted according to $C^R$ for both people and groups. As we can see, for both people and groups, the re-ordered matrix recovers maximally similar communities of nodes, where the similarity is based on their shared (degree-weighted) connections to entities in the other mode.

@@

>>>>

## CA Reveals Dual Communities
![](Plots/ca-sim-slide.png)

::: {.notes}
To fix the intuition, the top-left panel (a) of the figure shows a heatmap representation of the group-size weighted similarity matrix $S_p$ (for people); the top-right panel (b) shows the same plot for the activity-weighted similarity matrix $S_g$ (for groups). In both figures, darker squares indicate more similar node pairs, and closer to white indicate less similarity. Moreover, the rows of each matrix are sorted according to $C^R$ for both people and groups. As we can see, for both people and groups, the re-ordered matrix recovers maximally similar communities of nodes, where the similarity is based on their shared (degree-weighted) connections to entities in the other mode.

@@

## Thanks!

[https://github.com/olizardo/correspondence-analysis-two-mode-networks](https://github.com/olizardo/correspondence-analysis-two-mode-networks)

olizardo@soc.ucla.edu
